
\begin{thebibliography}{99} % Bibliography - this is intentionally simple in this template

\bibitem {W. C. Röntgen}
W. C. Röntgen. Ueber eine neue Art von Strahlen // Sonderabbdruck aus den Sitzungsberichten der Würzburger Physik.medic. Gesellschaft. — 1895;

\bibitem {Silverstein}
Silverstein E, Burmeister J, Fullerton G. SDAMPP student guide to a medical physics career. Alexandria, VA: Society of Directors of Academic Medical Physics Programs; 2016;

\bibitem {USGAO 2014}
U.S. Government Accountability Office. Federal workforce: recent trends in federal civilian employment and compensation. Washington, DC: GAO;14 -- 215; 2014;

\bibitem {HPS 2013}
Health Physics Society. Health physics education reference book. Health Physics Society Academic Education Committee. McLean, VA: HPS; 2010;

\bibitem {NCRP 2015}
National Council on Radiation Protection and Measurements. Where are the radiation professionals (WARP)? Bethesda, MD: NCRP; Statement No. 12; 2015;

\bibitem {Mills MD.2014} 
Mills MD. The meaning of the MS degree in medical physics, part 3. 2014;

\bibitem {RP174}
European Commission. Radiation Protection №174. Directorate-General for Energy Directorate D — Nuclear Safety \& Fuel Cycle Unit D.3 — Radiation Protection
2014;

\bibitem {IOMP}
International Organization for Medical Physics. Organization. Athens, Greece: IOMP; 2016. Available at www.iomp.org/? q=content/organisation. Accessed 9 August 2016;

\bibitem {AAPM1}
American Association of Physicists in Medicine. Professional survey report, calendar year 2015. College Park, MD: AAPM; 2016a;

\bibitem {Lievens}
Lievens Y., and etd.. Radiotherapy staffing in the European countries: final results from the ESTRO-HERO survey. Radiother Oncol 112:178–186; 2014;


\bibitem {Костылёв}
Костылёв, В.А., Наркевич, Б.Я.. Радиационная медицинская физика: прошлое, настоящее и будущее. Медицинская радиология и радиационная безопасность. -- 2006, --  Том 51, N1;

\bibitem {Тарутин}
Патыко, Д.. Нужны ли в больницах медицинские физики? -- Медицинский вестник. -- 2019. -- N 39 от 3 октября. -- с. 4;

\bibitem {AAPM 2016b}
American Association of Physicists in Medicine. Medical physicist. Definition of a qualified medical physicist. 2016b. Available at \href{https://w3.aapm.org/medical_physicist/fields.php}{Definition of a Qualified Medical Physicist}. Accessed 9 August 2016;

\bibitem {Newhauser}
Wayne D. Newhauser. The Medical Physics workforce. Department of Physics and Astronomy, Louisiana State University and Mary Bird Perkins Cancer Center, 439‐B Nicholson Hall, Tower Drive, Baton Rouge, LA 70803‐4001.

 
%\bibitem {No174}
%Guibelade E., Christifides S., Caruna C.J., Evans S., van der Putten W.
%\newblock Radiation Protection 174. European Guidelines on medical physics expert.  
%\newblock Directorate-General for Energy Directorate D — Nuclear Safety. Fuel Cycle Unit D.3 — Radiation Protection.
%2014;	%	{\em Human Nature}

%\bibitem [3]
\end{thebibliography}

